BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs

### 2013-11-11 tex/4-techniques.tex
Add download priority heuristic

\subsection{Enriching Scrapy}
Our project is build on top of Scrapy\TODO{link}, an open source python framework for web crawling. In addition to the extraction aspects of the project, we also enrich the framework with two components specific to blog post extraction: blog post identification and download policies.

Given an entry to a blog, Scrapy provides the infrastructure to look over all pages on the same domain. In order to identify the subset of pages that are actually blog posts, we build a "blog post identification" function that given an URL, returns whether or not it is a blog post. This function uses a regular expression that is constructed from the web feed entries: the only set of known blog post URLs.

Due to space constraints, more precise description and evaluation of these components where not included in this paper.

>>>>

\subsection{Enriching Scrapy}
Our project is build on top of Scrapy\TODO{link}, an open source python framework for web crawling. In addition to the extraction aspects of the project, we also enrich the framework with two components specific to blog-post extraction: blog-post identification and download priority heuristic.

Given an entry to a blog, Scrapy provides the infrastructure to look over all pages on the same domain. In order to identify the subset of pages that are actually blog-posts, we build a \emph{blog-post identification} function that given an URL, returns whether or not it is a blog-post. This function uses a regular expression that is constructed from the web feed entries: the only set of known blog-post URLs.

In order to efficiently deal with blogs with a large number non-blog-post pages, this mechanism is not sufficient. Indeed, after all pages identify as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts. To replace the naïve random walks, deaph first search and breath first search web site traversals, we use a priority queue with an heuristic function. Our \emph{download priority heuristic}works with a simple machine learning algorithm that given an URL predicts the number of links to blog-post the corresponding page will contain. Each time a page is dowloaded the number of blog-post links it contains is computer and given to the machine learning ...

Due to space constraints, more precise description and evaluation of these two components where not included in this paper.
